MSF_Groupwork-NBA_shotlog

### 2016-10-11 MSFGroupwork-NBAHotHand.Rmd
continued work on accuracy

@@

@@

# Find shooting percentage of each match

```{r}
# Reshape the dataframe

game <- cast(data = df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + LOCATION + player_name + W ~ FGM)

# Field Goal Attempts

game[, "FGA"] <- NA
for(i in 1:nrow(game)){
  game[i, "FGA"] <- game[i, "1"] + game[i, "0"]
}

# Find Feild Goal Percentage of each indivudual player in that match

game[, "FG.percentage"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG.percentage"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}
```

# Impact of Super Star Players

```{r}

# Pick out 8 of the best players in that regular season and create a new subset. Analyse how shooting percentage of these players can influence the result of a match.

super.star.list <- c("lebron james", "james harden", "russell westbrook", "stephen curry", "anthony davis", "blake griffin", "klay thompson", "lamarcus aldridge") # players picked out
super.star <- game[game$player_name %in% super.star.list, c("player_name", "W", "FGA", "FG.percentage")] # create a subset for these players

ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))
ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W))

# Replace "W" and "L" with 1 and 0 respectively, 
super.star[, "W"] <- as.character(super.star[, "W"])
for (i in 1:nrow(super.star)) {
  if (super.star[i, "W"] == "W") super.star[i, "W"] <- 1
  if (super.star[i, "W"] == "L") super.star[i, "W"] <- 0
}
super.star[, "W"] <- as.numeric(super.star[, "W"])

# Correlation test
t.test(super.star[, "W"], super.star[, "FGA"]) # this makes no sense...

# Linear regression
summary(lm(W ~ player_name + FGA, data = super.star))
summary(lm(W ~ player_name + FG.percentage, data = super.star))

@@

@@

#Create a function that gives us a vector of streaks for a specific player and game
player_and_game <- function(x, y) {
   player <- df[df[ ,'player_id'] == x & df[ ,'GAME_ID1'] == y, 'FGM']
   number_of_streaks(as.vector(player))
}

#Set a new data.frame for the 10 players with best performances(higher points)
ourtable <- head(pttsum2,10)

#Create a list that gives us the streaks of each player and game (10 best performances)
streak_per_player <- list()
j <- 1
for(i in ourtable$player_id) {
   streak_per_player[[j]] <- player_and_game(i, ourtable[ourtable[ ,'player_id'] == i, 'GAME_ID1'])
   j <- j + 1
}
streak_per_player

#Create a data frame for the strikes of each one of the 10 players (cannot create a data.frame including all of them, because each list has different length)
player1_df <- data.frame('streaks' = streak_per_player[[1]])
player2_df <- data.frame('streaks' = streak_per_player[[2]])
player3_df <- data.frame('streaks' = streak_per_player[[3]])
player4_df <- data.frame('streaks' = streak_per_player[[4]])
player5_df <- data.frame('streaks' = streak_per_player[[5]])
player6_df <- data.frame('streaks' = streak_per_player[[6]])
player7_df <- data.frame('streaks' = streak_per_player[[7]])
player8_df <- data.frame('streaks' = streak_per_player[[8]])
player9_df <- data.frame('streaks' = streak_per_player[[9]])
player10_df <- data.frame('streaks' = streak_per_player[[10]])
ourtable

#Visualisation for 10 players - distribution of each players' streaklengths
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[1,'player_name'])
ggplot(data = player2_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[2,'player_name'])
ggplot(data = player3_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[3,'player_name'])
ggplot(data = player4_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[4,'player_name'])
ggplot(data = player5_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[5,'player_name'])
ggplot(data = player6_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[6,'player_name'])
ggplot(data = player7_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[7,'player_name'])
ggplot(data = player8_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[8,'player_name'])
ggplot(data = player9_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[9,'player_name'])
ggplot(data = player10_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[10,'player_name'])

#We can see that the distribution of all players is right skewed and that all of them (especially player3) have some long shooting streaks. To prove/disprove the hot hand theory we need to examine the indipendence of the shots. If each shot that a player takes is independent of the next shot, then a missed/made shot will not affect the propability of succesfulness of the next shot. So, if consecutive shots are independent, we disprove hot hand theory, while if consecutive shots are dependent, we prove the hot hand theory.
#Simulation
shot_results <- c('made', 'missed')
simul_shooter <- sample(shot_results, size = nrow(player1_df), replace = TRUE, prob = c(0.45, 0.55))
simul_shooter

simul_shooter <- as.list(simul_shooter)
for(i in 1:length(simul_shooter)) {
   if(simul_shooter[i] == 'made') simul_shooter[i] <- 1
   else if(simul_shooter[i] == 'missed') simul_shooter[i] <- 0

}
simul_shooter
number_of_streaks(simul_shooter)
```

>>>>

# accuracy for Top 10 scoring players

@@

df[, "ACC_P_SEC"] <- as.numeric()

#Assign accuracy per second to main dataframe
for (i in 1:nrow(df)){
  for (j in 1:23){
    if (df$SHOT_CLOCK[i] >j & df$SHOT_CLOCK[i] <= j+1 & df$SHOT_CLOCK[i] != 99) df[i, "ACC_P_SEC"] <- acc[j, "Accuracy"]
  }
}

cov(df$ACC_P_SEC, df$SHOT_CLOCK)
cor.test(df$ACC_P_SEC, df$SHOT_CLOCK)

@@

#

```{r}
# Find shooting percentage of each match

# Trying to reshape...

library(reshape)
game <- cast(data = df, GAME_ID1 ~ SHOT_RESULT)
View(game)

#

Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
for(i in 21400001:21400908){
  j = i - 21400001 +1 # 
  game <- df[, df[, "GAME_ID1"] == i]
  home <- game[, game["LOCATION"] == "H"]
  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
  away <- game[, game["LOCATION"] == "A"]
  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
  FG_Percentage[j] <- home.p
  FG_Percentage[j + 1] = away.p
  Team[j] = "H"
  Team[j + 1] = "A"
}

@@

shotresult

@@

player_and_game <- function(x, y) {
   player <- df[df[ ,'player_id'] == x & df[ ,'GAME_ID1'] == y, 'FGM']
   number_of_streaks(as.vector(player))
}
player_and_game(202681, 21400681)

ourtable <- head(pttsum2,10)

list_per_player <- list()
j <- 1
for(i in ourtable$player_id) {
   streak_per_player[[j]] <- player_and_game(i, ourtable[ourtable[ ,'player_id'] == i, 'GAME_ID1'])
   j <- j + 1
}
streak_per_player
